Draft Manuscript

### 2022-09-20 Prereg_and_manuscript/manuscript.Rmd
manuscript now knits

csl: https://www.zotero.org/styles/ecology-letters
bibliography: references.bib

---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set
# I like to put all of my library calls here, each on a seperate line. I am not 
# sure if this is good or bad practice.
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(kableExtra)
```

**Title**: The title of your groundbreaking research paper

First Author^1^\*, Second Author^1^, Third Author^2,1^

1.  Dept. of Biology, Institution A, City, Province, Country

2.  Environmental Science Centre, Governmental Organisation, City, Province, Country

@@

email: first.author\@institutiona.ca (FA)

**Author Contributions:** FA conceived of the study, conducted the analyses, and wrote the original, and revised drafts of the manuscript. SA, and TA, helped with the draft manuscript and revisions and supplied guidance to FA. TA provided the data for the case study, contributed to the revisions, and assisted with the analysis of the case study data.

@@

**Key-words**: stuff, something

@@

## And example of adding citations in RMarkdown...

Ecologists have long recognized that some combinations of species are regularly found together, while other combinations occur infrequently [@Cole:1949dz; @Elton:1946dl].

The above format wraps the citation in brackets but if you want to reference the authors by name instead of just as a citation you can use this format instead (i.e., no square brackets around the cite key)

@Cole:1949dz and @Elton:1946dl both found that blah blah blah

@@

As with Pielou's Evenness [@Pielou:1967ea], Shannon's diversity index [@Shannon:1948iy]$(H)$ is normally calculated from species abundance values; however, for our purposes it is calculated from the column totals (species richness per sample) using the following equation...

$$
H_x = -S[P(i_x) \times ln(P(i_x))]
$$

where $x$ denotes which set of values we are using to calculate the index (observed, minimal or maximal), and $P(i_x)$ is the proportion of species that occur in each sample $(i)$.

@@

```{r table_01, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
penguin_sum <- penguins %>%
  group_by(island, year) %>%
  summarize(mean_body_mass_g = mean(body_mass_g, na.rm = TRUE)) %>% 
  ungroup()
kable(x = penguin_sum, 
      col.names = c("Island", "Year", "Mean Body Mass (g)")) %>%
  kable_styling(latex_options = "hold_position") 
# without the "hold_position" the table ends up at the top of the page
```

@@

![](figures/figure_01.png)

@@

```{r figure_02, echo=FALSE, message=FALSE, warning=FALSE}
penguins %>%
  select(species, body_mass_g, ends_with("_mm")) %>% 
  GGally::ggpairs(aes(color = species),
          columns = c("flipper_length_mm", "body_mass_g", 
                      "bill_length_mm", "bill_depth_mm")) +
  scale_colour_manual(values = c("darkorange","purple","cyan4")) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"))
```

@@

```{r file="../scripts/figure_03.R"}
# this code chunk calls an external script to generate the plot. If you
# want to load or run code not for a plot you could also use the following.
# Note that it does not seem to work for plots.
# source("../scripts/figure_03.R", local = knitr::knit_global())
```

>>>>

csl: https://www.zotero.org/styles/ecology-letters
bibliography: references.bib
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set
# Installing & Loading packages

#install.packages("groundhog")
library(groundhog)

# installing & loading packages
date <- "2022-09-02"
requiredPackages <-  c("here", "tidyverse","tidyr","Rfast","dplyr")

for (pkg in requiredPackages) {
  if (pkg %in% rownames(installed.packages()) == FALSE)
  {install.packages(pkg)}
  if (pkg %in% rownames(.packages()) == FALSE)
  {groundhog.library(pkg, date)}
}

```

**Title**: Can gradients in annual rainfall & forest type predict the distribution & abundance of 4 Ericaceous shrubs? - BIOL 548T LDP

Emma Menchons^1^\*

1.  Dept. of Botany, University of British Columbia, Vancouver, BC, Canada

@@

email: emma.menchions\@botany.ubc.ca

**Author Contributions:** EM conceived of the study, conducted the analyses, and wrote the original, and revised drafts of the manuscript.

@@

**Key-words**: Ecology, Ericaceae, LDP, Plant Ecology, Vegetation Mapping, Vegetation Patterns

@@

@@

@@

```{#{r table_01, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}

# without the "hold_position" the table ends up at the top of the page
```

@@

![]()

@@

```{#{r figure_02, echo=FALSE, message=FALSE, warning=FALSE}

```

@@

```{#{r file="../scripts/figure_03.R"}
# this code chunk calls an external script to generate the plot. If you
# want to load or run code not for a plot you could also use the following.
# Note that it does not seem to work for plots.
# source("../scripts/figure_03.R", local = knitr::knit_global())
```
